06-assessing_lime_explanations

### 2019-02-22 journals/06-assessing_lime_explanations.Rmd
knit journal 06 with the new training data

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
                      cache = TRUE)
```

@@

```{r}
library(gretchenalbrecht)
library(tidyverse)

@@

hamby224_sensitivity_joined <- read.csv("../data/hamby224_sensitivity_joined.csv")

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, warning = FALSE, 
                      error = FALSE, cache = TRUE)
```

@@

```{r}
# Load libraries
library(gretchenalbrecht)
library(tidyverse)

@@

hamby224_sensitivity_joined <- readRDS("../data/hamby224_sensitivity_joined.rds")
